%%% Seznam použité literatury (bibliografie)
%%%
%%% Pro vytváření bibliografie používáme bibTeX. Ten zpracovává
%%% citace v textu (např. makro \cite{...}) a vyhledává k nim literaturu
%%% v souboru literatura.bib.
%%%
%%% Příkaz \bibliographystyle určuje, jakým stylem budou citovány odkazy
%%% v textu. V závorce je název zvoleného souboru .bst. Styly plainnat
%%% a unsrt jsou standardní součástí latexových distribucí. Styl czplainnat
%%% je dodáván s touto šablonou a bibTeX ho hledá v aktuálním adresáři.

% \bibliographystyle{czplainnat}    %% Autor (rok) s českými spojkami
% \bibliographystyle{plainnat}    %% Autor (rok) s anglickými spojkami
\bibliographystyle{unsrt}       %% [číslo]

\renewcommand{\bibname}{Seznam použité literatury}

%%% Vytvoření seznamu literatury. Pozor, pokud jste necitovali ani jednu
%%% položku, seznam se automaticky vynechá.

\bibliography{literatura}

%%% Kdybyste chtěli bibliografii vytvářet ručně (bez bibTeXu), lze to udělat
%%% následovně. V takovém případě se řiďte normou ISO 690 a zvyklostmi v oboru.

\begin{thebibliography}{99}

% \bibitem{lamport94}
%   {\sc Lamport,} Leslie.
%   \emph{\LaTeX: A Document Preparation System}.
%   2. vydání.
%   Massachusetts: Addison Wesley, 1994.
%   ISBN 0-201-52983-1.

\bibitem{modalne okno}
Stack Exchange: What is a Modal Dialog Window?
\url{https://ux.stackexchange.com/questions/12045/what-is-a-modal-dialog-window}

\bibitem{gdpr}
Úrad pre~ochranu osobných údajov:~Všeobecné nariadenie o~ochrane osobných údajov~(GDPR).
\url{https://www.uoou.cz/obecne-narizeni-o-ochrane-osobnich-udaju-gdpr/ds-3938/p1=3938}

\bibitem{baas}
Cloudflare:~What is BaaS?
\url{https://www.cloudflare.com/en-gb/learning/serverless/glossary/backend-as-a-service-baas/}

\bibitem{spa}
MDN Web Docs Glossary:~SPA~(Single-page application).
\url{https://developer.mozilla.org/en-US/docs/Glossary/SPA}

\bibitem{seo}
Mailchimp glossary: What is SEO?
\url{https://mailchimp.com/marketing-glossary/seo/}

\bibitem{novateus}
Novateus: Single Page Applications, most discussed pros and cons.
\url{https://novateus.com/blog/single-page-applications-spas-most-discussed-pros-cons/}

\bibitem{cloudways}
Cloudways: How to Perform SEO for Single Page Applications.
\url{https://www.cloudways.com/blog/single-page-website-spa-seo/}

\bibitem{stats}
Oberlo: Most popular web browsers in 2023.
\url{https://www.oberlo.com/statistics/browser-market-share}

\bibitem{wa support}
Can I Use: WebAssembly.
\url{https://caniuse.com/wasm}

\bibitem{chromexpver1}
MSFN: Chrome 49 Update.
\url{https://msfn.org/board/topic/175404-chrome-49-update/}

\bibitem{chromexpver2}
Chrome Blog: November updates to Chrome platform support (2015).
\url{https://chrome.googleblog.com/2015/11/updates-to-chrome-platform-support.html}

\bibitem{chromexpver3}
Chrome Releases: September updates from (2015).
\url{https://chromereleases.googleblog.com/2015/09/}

\bibitem{mpa}
LinkedIn: Single-page application vs. Multi-page application.
\url{https://www.linkedin.com/pulse/single-page-application-vs-multi-page-what-better-your-/}

\bibitem{aspnetmvc}
Microsoft .NET: ASP.NET MVC Pattern.
\url{https://dotnet.microsoft.com/en-us/apps/aspnet/mvc}

\bibitem{components in aspnet mvc}
Stack Overflow: Creating reusable HTML view components using Razor in~ASP.NET MVC.
\url{https://stackoverflow.com/questions/23518499/creating-reusable-html-view-components-using-razor-in-asp-net-mvc}

\bibitem{blazor server}
Microsoft documentation: Blazor Server.
\url{https://learn.microsoft.com/en-us/aspnet/core/blazor/hosting-models?view=aspnetcore-7.0\#blazor-server}

\bibitem{relational db}
Microsoft Azure: Co je relační databáze?
\url{https://azure.microsoft.com/cs-cz/resources/cloud-computing-dictionary/what-is-a-relational-database/\#whatis}

\bibitem{nosql db}
Microsoft Azure: Databáze NoSQL~-- co je NoSQL?
\url{https://azure.microsoft.com/cs-cz/resources/cloud-computing-dictionary/what-is-nosql-database/}

\bibitem{nosql pros}
Coursera: Relational vs. Non-relational Database.
\url{https://www.coursera.org/articles/relational-vs-non-relational-database#2-when-to-use-a-relational-vs-a-non-relational-database}

\bibitem{relational model}
GeeksforGeeks: Relational Model in DBMS.
\url{https://www.geeksforgeeks.org/relational-model-in-dbms/}

\bibitem{microsoft sql server}
Microsoft: SQL Server 2022 comparison.
\url{https://www.microsoft.com/en-us/sql-server/sql-server-2022-comparison}

\bibitem{oracle database}
Oracle: Oracle Database XE.
\url{https://www.oracle.com/database/technologies/appdev/xe.html}

\bibitem{mysql}
MySQL: Community Server.
\url{https://dev.mysql.com/downloads/mysql/}

\bibitem{orm}
freeCodeCamp: What is an ORM~-- The Meaning of Object Relational Mapping Database Tools.
\url{https://www.freecodecamp.org/news/what-is-an-orm-the-meaning-of-object-relational-mapping-database-tools}

\bibitem{oop}
freeCodeCamp: The Four Pillars of Object-Oriented Programming.
\url{https://www.freecodecamp.org/news/four-pillars-of-object-oriented-programming/}

\bibitem{sanitization}
LinkedIn: How do you handle user input validation and sanitization to avoid SQL injection vulnerabilities?
\url{https://www.linkedin.com/advice/0/how-do-you-handle-user-input-validation-sanitization}

\bibitem{dapper repo}
GitHub: Dapper repository.
\url{https://github.com/DapperLib/Dapper/#performance}

\bibitem{code first}
Entity Framework Tutorial: What is Code-First?
\url{https://www.entityframeworktutorial.net/code-first/what-is-code-first.aspx}

\bibitem{csharp corner}
C\# Corner: Dapper vs. Entity Framework Core.
\url{https://www.c-sharpcorner.com/article/dapper-vs-entity-framework-core/}

\bibitem{timer}
Microsoft documentation: \verb|Timer| Class.
\url{https://learn.microsoft.com/en-us/dotnet/api/system.timers.timer?view=net-6.0}

\bibitem{dispose}
Microsoft documentation: \verb|Timer.Dispose| Method.
\url{https://learn.microsoft.com/en-us/dotnet/api/system.threading.timer.dispose?view=net-6.0}

\bibitem{dependency injection}
Microsoft documentation: ASP.NET Core Blazor dependency injection.
\url{https://learn.microsoft.com/en-us/aspnet/core/blazor/fundamentals/dependency-injection}

\bibitem{hosted service}
Microsoft documentation: \verb|IHostedService| interface.
\url{https://learn.microsoft.com/en-us/aspnet/core/fundamentals/host/hosted-services?view=aspnetcore-7.0&tabs=visual-studio\#ihostedservice-interface}

\bibitem{background service}
Microsoft documentation: \verb|BackgroundService| base class.
\url{https://learn.microsoft.com/en-us/aspnet/core/fundamentals/host/hosted-services?view=aspnetcore-7.0&tabs=visual-studio\#backgroundservice-base-class}

\bibitem{background service for long running tasks}
Compositional IT: Background Tasks in .NET.
\url{https://www.compositional-it.com/news-blog/background-tasks-in-net}

\bibitem{executeasync}
Microsoft documentation: \verb|ExecuteAsync(CancellationToken)| Method of \verb|BackgroundService| Class.
\url{https://learn.microsoft.com/en-us/dotnet/api/microsoft.extensions.hosting.backgroundservice.executeasync?view=dotnet-plat-ext-7.0}

\bibitem{start}
Microsoft documentation: \verb|Timer.Start| Method.
\url{https://learn.microsoft.com/en-us/dotnet/api/system.timers.timer.start}

\bibitem{elapsed}
Microsoft documentation: \verb|Timer.Elapsed| Event.
\url{https://learn.microsoft.com/en-us/dotnet/api/system.timers.timer.elapsed}

\bibitem{addhostedservice}
Microsoft documentation: Implement the \verb|IHostedService| interface.
\url{https://learn.microsoft.com/en-us/dotnet/core/extensions/timer-service?pivots=dotnet-7-0}

\bibitem{migrations}
Microsoft documentation: Migrations Overview.
\url{https://learn.microsoft.com/en-us/ef/core/managing-schemas/migrations/?tabs=dotnet-core-cli}

\bibitem{api}
Amazon: What Is An API (Application Programming Interface)?
\url{https://aws.amazon.com/what-is/api/}

\bibitem{authorizeview}
Microsoft documentation: \verb|AuthorizeView| component.
\url{https://learn.microsoft.com/en-us/aspnet/core/blazor/security/?view=aspnetcore-7.0\#authorizeview-component}

\bibitem{authorize attribute}
Microsoft documentation: \verb|[Authorize]| attribute.
\url{https://learn.microsoft.com/en-us/aspnet/core/blazor/security/?view=aspnetcore-7.0\#authorize-attribute}

\bibitem{sfdialogprovider}
Syncfusion documentation: \verb|SfDialogProvider| Class.
\url{https://help.syncfusion.com/cr/blazor/Syncfusion.Blazor.Popups.SfDialogProvider.html}

\bibitem{sfdialogservice}
Syncfusion documentation: \verb|SfDialogService| Class.
\url{https://help.syncfusion.com/cr/blazor/Syncfusion.Blazor.Popups.SfDialogService.html}

\bibitem{mysql navod}
MySQL: Installing and Upgrading MySQL.
\url{https://dev.mysql.com/doc/refman/8.0/en/installing.html}

\bibitem{visual studio}
Microsoft: Visual Studio.
\url{https://visualstudio.microsoft.com/vs/}

\bibitem{standard connection string}
ConnectionStrings: MySQL connection strings.
\url{https://www.connectionstrings.com/mysql/}

\bibitem{license key}
Syncfusion: Generate Syncfusion Blazor License Key.
\url{https://blazor.syncfusion.com/documentation/getting-started/license-key/how-to-generate}

\bibitem{app password}
Google support: Sign in with app passwords.
\url{https://support.google.com/accounts/answer/185833?hl=en}

\bibitem{azure}
Microsoft Azure: Homepage.
\url{https://azure.microsoft.com/en-us/homepage-b/}

\bibitem{blazorserveraspnet}
Microsoft documentation: Host and deploy Blazor Server.
\url{https://learn.microsoft.com/en-us/aspnet/core/blazor/host-and-deploy/server?view=aspnetcore-7.0#deployment}

\bibitem{deploy}
Microsoft documentation: Deploy an ASP.NET Core and Azure SQL Database app to Azure App Service.
\url{https://learn.microsoft.com/en-gb/azure/app-service/tutorial-dotnetcore-sqldb-app}
\end{thebibliography}

\hspace{1cm}

Dostupnosť online zdrojov bola overená dňa 20.7.2023.
